%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Systems Administrator \& Infrastructure Engineer} % Job title
    {\href{http://genome.duke.edu}{Duke Center for Genomic and Computational Biology}} % Organization
    {Duke University} % Location
    {2014 - present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Administrated 1.5 Petabytes of NetApp FAS and E-Series storage.}
        \item {Administrated and advised researchers and graduate students on using our 3744 core HPC cluster.}
        \item {Tuned hardware and GPFS software for better performance.}
        \item {Transitioned center from using VMware to user controlled OpenStack deployment of research virtual machines.}
        \item {Integrated Ansible into manually deployed systems the previous staff had deployed by hand.}
        \item {Involved in the center's \href{http://genome.duke.edu/gcb-academy}{GCB Academy} by teaching HPC section of two day workshops.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Systems Administrator} % Job title
    {\href{http://cyverse.org/}{CyVerse (formerly iPlant Collaborative)}} % Organization
    {University of Arizona} % Location
    {2013 - 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Deployed new OpenStack installation at TACC.}
        \item {Maintained existing OpenStack installation at the University of Arizona.}
        \item {Responsible for software upgrades and monitoring of \href{http://irods.org/}{iRODS} based Data Store.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Systems Programmer} % Job title
    {\href{http://eeb.arizona.edu/}{Ecology and Evolutionary Biology}, \href{https://u.osu.edu/viruslab/}{Sullivan Lab}} % Organization
    {University of Arizona} % Location
    {2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Administration of shared HPC cluster.}
        \item {Installation of genomics applications on the cluster.}
        \item {Porting of lab developed pipelines to run within the iPlant/CyVerse infrastrucutre.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Systems Programmer} % Job title
    {\href{http://eeb.arizona.edu/}{Ecology and Evolutionary Biology}, Sanderson Lab} % Organization
    {University of Arizona} % Location
    {2007 - 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Installation and administraion of 288 core HPC cluster for the lab.}
        \item {Installation and configuration of 9 panel visualization wall using software from the \href{http://www.sdsc.edu/}{San Diego Supercomputer Center} and the \href{https://www.evl.uic.edu/}{Electronic Visualization Lab} at University of Illinois at Chicago.}
        \item {Programmed new and parallelized existing portions of the computing pipeline for a large scale phyloinformatics project in Perl.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Bioinformaticist} % Job title
    {The Field Museum - Zoology} % Organization
    {\href{https://www.fieldmuseum.org/}{The Field Museum}} % Location
    {2009 - 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Administered the museum's high performance computing cluster.}
        \item {Developed a Ruby on Rails application for data collection on the \href{https://www.fieldmuseum.org/emerging-pathogens-project}{Emerging Pathogens Project}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {System Administrator} % Job title
    {\href{https://ist.ualberta.ca/}{Academic Information and Communication Technologies}} % Organization
    {University of Alberta} % Location
    {2005 - 2007} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {System administrator for several departmental and research projects on campus running a mixture of Solaris, AIX and Linux operating systems.}
        \item {Secondary contact for many critical Oracle instances.}
        \item {Consulted on and configured Linux based high performance computing clusters.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {System Administrator} % Job title
    {\href{http://folkwaysalive.ualberta.ca/}{Folkways Alive!}} % Organization
    {University of Alberta} % Location
    {2005} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Assisted with system and network administration during project start up.}
        \item {Installation and support for Linux servers, Sun Ray thin clients, OpenBSD firewalls, Cisco wireless and HP ProCurve Gigabit network.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer/System Administrator} % Job title
    {Text Analysis Portal for Research} % Organization
    {University of Alberta} % Location
    {2003 - 2005} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Assisted in drafting server RFP and vendor selection during initial hardware purchase.}
        \item {System administration for Linux and Solaris servers.}
        \item {Implemented incremental network backup scripts utilizing open source software.}
        \item{Ongoing software development and consultation with research projects.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {System Administrator} % Job title
    {Bruce Rannala's Research Group} % Organization
    {University of Alberta} % Location
    {2002 - 2003} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Installation and administration of 36 CPU Linux high performance computing cluster.}
        \item {Managed network, firewall, file and print services for lab.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {GE Fanuc} % Organization
    {Edmonton, Alberta} % Location
    {2001 - 2002} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Team member developing Synergy, a framework of components, tools and processes to enable rapid development and deployment of web-based manufacturing execution system solutions.}
        \item {Development done using a number of J2EE technologies including XML, XSLT, SOAP, Java Applets, JSP and Servlets.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Programmer/Analyst} % Job title
    {System and Technology Services, Department of Education, Training and Youth} % Organization
    {Winnipeg, Manitoba} % Location
    {1999 - 2001} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Programmer on a J2EE web-based application for collecting and processing student loan applications for Manitoba Student Aid.}
        \item {Implemented version control software for all software development projects.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
