%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Teaching}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Instructor} % Role
    {\href{http://duke-gcb.github.io/SciComp-Mar-2016/}{GCB Academy - Introduction to Scientific Computing for Genomics}} % Event
    {Duke University, Durham, NC} % Location
    {Mar. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Taught section on staging jobs and data for HPC.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Instructor} % Role
    {\href{http://duke-gcb.github.io/SciComp-Oct-2015/}{GCB Academy - Introduction to Scientific Computing for Genomics}} % Event
    {Duke University, Durham, NC} % Location
    {Oct. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Taught section on staging jobs and data for HPC.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Instructor} % Role
    {\href{http://duke-gcb.github.io/SciComp-Feb-2015/}{GCB Academy - Introduction to Scientific Computing for Genomics}} % Event
    {Duke University, Durham, NC} % Location
    {Feb. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Taught section on staging jobs and data for HPC.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Instructor} % Role
    {\href{http://kcranston.github.io/2015-01-29-ncsu/}{Software Carpentry Bootcamp}} % Event
    {North Carolina State University, Raleigh, NC} % Location
    {Jan. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Taught sections on Python and version control with Git.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Helper} % Role
    {\href{http://software-carpentry.org/blog/2014/05/our-first-data-carpentry-workshop.html}{Data Carpentry Bootcamp}} % Event
    {Duke University, Durham, NC} % Location
    {May. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Was a helper at the inaugural Data Carpentry bootcamp at the National Evolutionary Synthesis Center.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Teacher Training} % Role
    {Software Carpentry Teacher Training} % Event
    {Mozilla, Toronto, ON} % Location
    {Apr. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Took three day Software Carpentry teacher training course.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Workshop facilitator} % Role
    {Carolina Farm Stewardship Sustainable Agriculture Conference} % Event
    {Sheraton Imperial Hotel, Durham, NC} % Location
    {Nov. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s)
      \item {Co-presented at the farmhack workshop on microcontrollers and other electronics useful in automation projects.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Instructor} % Role
    {\href{http://swcarpentry.github.io/2013-08-22-ku/}{Software Carpentry Bootcamp}} % Event
    {University of Kansas, Lawrence, KS} % Location
    {Aug. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Taught section on Python.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Helper} % Role
    {Software Carpentry Bootcamp} % Event
    {University of Arizona, Tucson, AZ} % Location
    {Apr. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Helper at the iPlant sponsored Software Carpentry workshop.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
